Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-14 paper/main.tex
table paper included

>>>>

\begin{tabular}{llrrr}
\toprule
Problem &                instance &  Fitness CEGO &  Fitness UMM &  Improvement \\
\midrule
    LOP &  lop/RandA1/N-t1d100.01 &       78696.6 &      76119.6 &     0.032746 \\
    LOP &  lop/RandA1/N-t1d100.02 &       79686.5 &      76827.7 &     0.035876 \\
    LOP &  lop/RandA1/N-t1d150.01 &      187605.5 &     179508.3 &     0.043161 \\
    LOP &  lop/RandA1/N-t1d150.02 &      184320.9 &     177592.8 &     0.036502 \\
    LOP &  lop/RandA1/N-t1d200.01 &      335391.1 &     323513.6 &     0.035414 \\
    LOP &  lop/RandA1/N-t1d200.02 &      333149.5 &     319675.8 &     0.040443 \\
    LOP &  lop/RandA2/N-t2d150.01 &       24682.7 &      15297.7 &     0.380226 \\
    LOP &  lop/RandA2/N-t2d150.02 &       24250.8 &      14724.9 &     0.392808 \\
   PFSP &          pfsp/rec05.txt &        1317.9 &       1330.7 &    -0.009712 \\
   PFSP &          pfsp/rec13.txt &        2128.2 &       2158.7 &    -0.014331 \\
   PFSP &          pfsp/rec19.txt &        2398.6 &       2405.1 &    -0.002710 \\
    QAP &           qap/kra32.dat &      115907.0 &     116320.0 &    -0.003563 \\
    QAP &           qap/nug12.dat &         624.2 &        660.4 &    -0.057994 \\
    QAP &           qap/nug30.dat &        7486.8 &       7474.0 &     0.001710 \\
    QAP &           qap/tho30.dat &      192416.0 &     191482.0 &     0.004854 \\
\bottomrule
\end{tabular}
